<style>
body {font-family: "Times New Roman"}
</style>

<center><h1>Machine Learning Lab</h1></center>
<center><h2>Spring 2021</h2></center>

<h5>In this lab, we will be working with a wheat seed dataset compiled by a research group in Lublin, Poland. The dataset contains seven attributes:</h5>
1. area 
2. perimeter 
3. compactness
4. length of kernel
5. width of kernel
6. asymmetry coefficient
7. length of kernel grove

<h5>Three varieties of wheat were used:</h5>
1. Kama
2. Rosa
3. Canadian

<h5>The dataset contains 70 randomly selected observations from each wheat variety.</h5>

### Load the R packages that we will use in this lab
```{r}
library(ggplot2)
```

### Set your working directory to where you would like to work
This should be where you have saved the data.

```{r}
setwd("~/Documents/wild_rice") # Change the path to reflect the location of the data on your machine.
```

If you are working in Rstudio, you can also change your directory by going to the ```Session``` drop-down menu and selecting "Set Working Directory"

### Read in the data
```{r}
x <- read.table("seeds_dataset.txt")
```

We can use the ```dim()``` function to check the dimensions of our dataset. There are 210 observations (rows) which matches our expectation of 70 observations of 3 wheat varieties. The reason there are 8 columns instead of 7 is because the 8th column identifies the wheat variety.
```{r}
dim(x)
```