<style>
body {font-family: "Times New Roman"}
</style>

<center><h1>Machine Learning Lab</h1></center>
<center><h2>Spring 2021</h2></center>

<h5>In this lab, we will be working with a wheat seed dataset compiled by a research group in Lublin, Poland. The dataset contains seven attributes:</h5>
1. area 
2. perimeter 
3. compactness
4. length of kernel
5. width of kernel
6. asymmetry coefficient
7. length of kernel groove

<h5>Three varieties of wheat were used:</h5>
1. Kama
2. Rosa
3. Canadian

<h5>The dataset contains 70 randomly selected observations from each wheat variety.</h5>

### Load the R packages that we will use in this lab
```{r}
library(data.table)
library(ggplot2)
library(GGally)
```

### Set your working directory to where you would like to work
This should be where you have saved the data.

```{r}
setwd("~/Documents/wild_rice") # Change the path to reflect the location of the data on your machine.
```

If you are working in Rstudio, you can also change your directory by going to the ```Session``` drop-down menu and selecting "Set Working Directory"

### Read in the data
```{r}
x <- read.table("seeds_dataset.txt")
```

Convert from a data frame to data.table because it is easier to work with.
```{r}
x <- as.data.table(x)
```

Assign meaningful names to each column since they weren't in the origina data file.
```{r}
names(x) <- c("area", "perimeter", "compactness", "kernel.length", "kernel.width", 
"asymmetry.coef", "groove.length", "cultivar")
```

Change the cultivar ID from numbers to cultivar names to make it easier to understand.
```{r}
x[, cultivar := sub(1, "Kama", cultivar)]
x[, cultivar := sub(2, "Rosa", cultivar)]
x[, cultivar := sub(3, "Canadian", cultivar)]
```

We can use the ```dim()``` function to check the dimensions of our dataset. There are 210 observations (rows) which matches our expectation of 70 observations of 3 wheat varieties. The reason there are 8 columns instead of 7 is because the 8th column identifies the wheat variety.
```{r}
dim(x)
```

We can also get a summary of the distribution of our data using the ```summary()``` function.
```{r}
summary(x)
```

Continue to examine the data.
```{r}
ggpairs(x,
        columns = 1:4, aes(color=cultivar, alpha=0.5),
        axisLabels = 'none', switch = 'both') +
        theme_bw()
```